### 2019-05-09 manuscript.rmd
preparing for submission, clean manuscript, clean code

#PIC correlations by character, to get significance
PICp = as.data.frame(matrix(nrow=ncol(C), ncol=ncol(C)))
colnames(PICp) = colnames(C)
rownames(PICp) = colnames(C)
for(i in 2:ncol(sharedmean_logs)){
  Ci = sharedmean_logs[,i]
  names(Ci) = sharedmean_logs$Species
  Ci = Ci[!is.na(Ci)]
  for(j in 2:ncol(sharedmean_logs)){
    Cj = sharedmean_logs[,j]
    names(Cj) = sharedmean_logs$Species
    Cj = Cj[!is.na(Cj)]
    Cj = Cj[which(names(Cj) %in% names(Ci))]
    Ci = Ci[which(names(Ci) %in% names(Cj))]
    if(i!=j){
      ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(Cj))))
      class(ctree)<-"phylo"
      pic_i = pic(Ci, ctree)
      pic_j = pic(Cj, ctree)
      cor.test(pic_i, pic_j)$p.value %>% round3() -> PICp[i-1,j-1]
    }
    else PICp[i-1,j-1]<-NA
  }
}
write.csv(PICp, "PICcorrelations_pvalues.csv")

>>>>

#PIC correlations by character, to get significance
PICp = as.data.frame(matrix(nrow=ncol(C), ncol=ncol(C)))
colnames(PICp) = colnames(C)
rownames(PICp) = colnames(C)
for(i in 2:ncol(sharedmean_logs)){
  Ci = sharedmean_logs[,i]
  names(Ci) = sharedmean_logs$Species
  Ci = Ci[!is.na(Ci)]
  for(j in 2:ncol(sharedmean_logs)){
    Cj = sharedmean_logs[,j]
    names(Cj) = sharedmean_logs$Species
    Cj = Cj[!is.na(Cj)]
    Cj = Cj[which(names(Cj) %in% names(Ci))]
    Ci = Ci[which(names(Ci) %in% names(Cj))]
    if(i!=j){
      ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(Cj))))
      class(ctree)<-"phylo"
      pic_i = pic(Ci, ctree)
      pic_j = pic(Cj, ctree)
      cor.test(pic_i, pic_j)$p.value %>% round3() -> PICp[i-1,j-1]
    }
    else PICp[i-1,j-1]<-NA
  }
}
#write.csv(PICp, "PICcorrelations_pvalues.csv")
